Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-08-04 dataset_comparison.Rmd
Fix call for Terrier plots

# call Terrier plots
knitr::include_graphics("./results/secondary/phoenix/windowed-crqa/target-windowed_all.png")
knitr::include_graphics("./results/secondary/phoenix/windowed-crqa/source_target-windowed_all.png")

>>>>

# call Terrier plots
knitr::include_graphics("./results/secondary/terrier/windowed-crqa/target-windowed_all.png")
knitr::include_graphics("./results/secondary/terrier/windowed-crqa/source_target-windowed_all.png")
